--- 
title: "Convex Optimization Notes"
author: "Fan Jiang"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib]
biblio-style: apalike
link-citations: yes
description: "This is my notes while studying Prof. Stephen Boyd's convex optimization course."
---

# Preface {.unnumbered}

This is my notes while studying Prof. Stephen Boyd's convex optimization course ([link](https://www.youtube.com/playlist?list=PL3940DD956CDF0622)).

I will try my best covering his points and add figures and code that illustrates his ideas.

You will need the following tools to compile it.

The **bookdown** and **reticulate** package can be installed from CRAN:

```{r eval=FALSE}
install.packages("bookdown")
install.packages("reticulate") # for Python snippets
```

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
# knitr::write_bib(c(
#   .packages(), 'bookdown', 'knitr', 'rmarkdown'
# ), 'packages.bib')
knitr::opts_chunk$set(engine.path = list(
  python = '/usr/local/bin/python3'
))
```
